---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GroupMeanSummarization

The goal of 'R' Package Group Mean Summarization is to provides a **function to calculate the arithmetic mean**. Further, the user can choose to group the data at any single or multiple levels to calculate the mean over those groupings. Moreover, for convenience, the user can select data grouping via column index(es) or column name(s).

## Installation

You can install the development version of Group Mean Summarization like so:

``` {r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/GroupMeanSummarization")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
suppressPackageStartupMessages(library(GroupMeanSummarization))
suppressPackageStartupMessages(library(tidyverse))

## Creating sample data
(sampleData <- data.frame(Name = c("Vir", "Shreya", "Kabir", "Vir", "Kabir"),
                 TransactionCity = c("Vancouver", "Vancouver", "California", "Seattle", "California"),
                 TransactionCost = c(100, 50, 80, 100, 40),
                 ItemsPurchased = c(4,1,4,6,2)
                 ))

## Summary of arithmetic mean on sample data by person
Group_mean_summarization(sampleData, "Name")

## Summary of arithmetic mean on sample data by city and person
Group_mean_summarization(sampleData, c(2,1))
```







